Supplementary Material

### 2022-11-10 paper/paper/SPIE/article.tex
[WIP]

We perform a \textit{multiverse
analysis}\cite{steegenIncreasingTransparencyMultiverse2016} to assess the
overall predictive potential of the various eigenfeatures across all
previously-mentioned analytic choices. That is, for each combination of
comparison task and classifier, we use 5-fold cross validation, and use the
mean AUROC (mAUROC) across folds as our metric to evaluate feature predictive utility.

@@

In addition, each analytic factor could produce an interaction. For example, it
could be that trimming impacts the overall mAUROC distribution only at a
certain preprocessing level and for certain feature slicing. However, there are
too many potential interactions to present, so we limit our presentation to the
most significant ones.  As there are a large number of features, we also
summarize patterns of results across two abstract levels of feature
groupings—"coarse", and "fine"—shown in Table \ref{tab:features}.

Finally, it makes sense to exclude classification tasks or an analytic factor
from summaries if there is no evidence that the classification task is solvable
in general, or for that factor. We take as lack of evidence of solvability an
mAUROC distribution that is either (1) roughly symmetric and has mean and
median close to 0.5, or (2) with median and mode less than 0.5.

@@

\subsection{Effect of Preprocessing}
At a coarse level, slice time correction followed by motion correction tended
to slightly increase the predictive utility of the eigenfeatures (Figure
\ref{fig:preproc}) relative to brain extraction only. Subsequent registration
following these steps did not generally impact mAUROC distributions further,
except in the \code{task\_attend v task\_nonattend} comparison, where
registration reduced the predictive utility of the eigenfeatures (Figure
\ref{fig:preproc}, second-last column). When examining features more finely, it
is clear that preprocessing most impacts the mAUROC distribution of the largest
and central eigenvalues ("eigs middle" and "eigs max" in Figure
S\ref{S-fig:fine-preproc})

@@

\subsection{Effect of Trimming}
Trimming based on numerical precision (see Section \ref{sec:rmt-features} and
Appendix \ref{sec:trimming}), did not result in meaningfully different mAUROC
distributions in any case (Figure S\ref{S-fig:fine-trim}).   While there was no
clearly observable differences between the mAUROC distributions depending on
whether

@@

First not non-predictable data, and then no longer discuss it in subsequent features.

\subsection{Normalization}
NO meaningful effect of normalization on AUROC distributions at level of gross feature, or feature
group, so can safely ignore this.
NO meaningful effect of normalization for any feature group by classifier either, so
normalization doesn't seem to matter here.
Maybe add table of correlations by groupings here

>>>>

We perform a \textit{multiverse
analysis}\cite{steegenIncreasingTransparencyMultiverse2016} to assess the
overall predictive potential of the various eigenfeatures across all
previously-mentioned analytic choices. That is, for each combination of
comparison task, classifier, and analytic choices, we use 5-fold cross
validation, and use the mean AUROC (mAUROC) across folds as our metric to
evaluate feature predictive utility.

@@

In addition, each analytic factor could produce an interaction. For example, it
could be that trimming impacts the overall mAUROC distribution only at a
certain preprocessing level and for certain feature slicing. However, there are
too many potential interactions to present, so we limit our presentation to the
most significant ones.  As there are a large number of features, we also
summarize patterns of results across two abstract groupings of features
("coarse", and "fine") shown in Table \ref{tab:features}.

It is also important to exclude a classification task or an analytic factor
from summaries if there is no evidence that the classification task is solvable
in general, or for that factor. We take as lack of evidence of solvability an
mAUROC distribution that is either (1) roughly symmetric and has mean and
median close to 0.5, or (2) with median and mode less than 0.5.

@@

\subsection{Effect of Preprocessing}
At a coarse level, slice time correction followed by motion correction tended
to slightly increase the predictive utility of the eigenfeatures (Figure
\ref{fig:preproc}) relative to brain extraction only. Subsequent registration
following these steps did not generally impact mAUROC distributions further,
except in the \code{task\_attend v task\_nonattend} comparison, where
registration reduced the predictive utility of the eigenfeatures (Figure
\ref{fig:preproc}, second-last column). When examining features more finely, it
is clear that preprocessing most impacts the mAUROC distribution of the largest
and central eigenvalues ("eigs middle" and "eigs max" in Figure
S\ref{S-fig:fine-preproc}).

@@

\subsection{Normalization}
There was no visible effect of normalization on mAUROC distributions at any
summary level.

\subsection{Effect of Trimming}
Trimming based on numerical precision (see Section \ref{sec:rmt-features} and
Appendix \ref{sec:trimming}), did not result in meaningfully different mAUROC
distributions in any case (Figure S\ref{S-fig:fine-trim}). However, trimming
away the largest, or both largest and smallest eigenvalues, generally had a
significant positive effect on the predictive quality of RMT features, most
especially for RMT features involving the unfolded eigenvalues. When employing
these trimming methods, these features were consistently more predictive than
not.

@@

\subsection{Effect of Slicing}
Features were most predictive when using either the largest 5 or 10\% or middle
25\% ("max-05", "max-10" and "mid-25" in Figure
\ref{S-fig:best-params-slicing}), and least predictive when features primarily
involved the smallest eigenvalues.

\subsection{Best Case Scenario}
Viewing all the impactful analytic choices as tunable hyperparameters, and
selecting the overall "best" hyperparameters of \(\text{trimming} \in
\{\text{middle}, \text{largest}\}\), \(\text{degree} \in \{3, 9\}\),
\(\text{preprocessing} \in \{\text{MotionCorrect}, \text{MNIRegister}\}\),
\(\text{slicing} \in \{\text{"max-10"}, \text{"mid-25"}\} \) and
restricting to only the "unfolded" RMT feature, results in the mAUROC
distributions in Figure S\ref{S-fig:best-params}. Using these analytic choices,
the \code{depress v control} comparison in the \textit{Depression} dataset
becomes weakly predictable, and the smoothed eigenvalue features tend to
closely follow the unfolded eigenvalues in predictive utility.

### 2022-11-10 paper/paper/SPIE/supplementary.tex
[WIP]

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{best_rmt_params_by_subgroup.png}
\end{center}
\caption
{ \label{fig:best-params}
Distributions of mAUROCs when choosing ``best'' analytic choices and features.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{best_rmt_params_by_subgroup_and_slicing.png}
\end{center}
\caption
{ \label{fig:best-params-slicing}
Distributions of mAUROCs when choosing ``best'' analytic choices and features, by slicing.}
\end{figure}
